---
title: "Codebook"
author: "Laercio Gil"
date: "01/08/2017"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
tidy <- read.table("tidy.txt", sep = " ")
```

##Description of the variables in the tidy.txt file

General description of the file including:

- Dimensions of the dataset
- Summary of the data
- Variables present in the dataset

(you can easily use Rcode for this, just load the dataset and provide the information directly form the tidy data file)

###Variable 1 (repeat this section for all variables in the dataset)

Short description of what the variable describes.

Some information on the variable including:

- Class of the variable
- Unique values/levels of the variable
- Unit of measurement (if no unit of measurement list this as well)
- In case names follow some schema, describe how entries were constructed (for example time-body-gyroscope-z has 4 levels of descriptors. Describe these 4 levels).

(you can easily use Rcode for this, just load the dataset and provide the information directly form the tidy data file)

This is an introductory sentence with absolutely no interest.

###Key Variables
```{r KeyVariables, results="asis", eval=TRUE}
for (varname in names(tidy[1:2])) {
  var <- tidy[, varname]
  cat("
#### **`", varname,"`**
* **Class**: ", class(var),"
* **Summary**: 
<pre>")
if (is.numeric(var)) {
  print(table(var))
} else {
  print(summary(var))
}
cat("</pre>

***
")
}
```

###Measure Variables
```{r MeasureVariables, results="asis", eval=TRUE}
for (varname in names(tidy[3:length(tidy)])) {
  var <- tidy[, varname]
  cat("
#### **`", varname,"`**
* **Class**: ", class(var),"
* **Summary**: 
<pre>")
print(summary(var))
cat("</pre>

***
")
}
```


####Notes on variable 1:
If available, some additional notes on the variable not covered elsewehere. If no notes are present leave this section out.